---
title: "UpSetR motif Enh DAR DMRs intersection within each Layer: show how similar they are"
output:
  word_document: default
  html_notebook: default
---

  -We are checking if Enh DAR DMR motifs are lineage-specific within laeyr, e.g. contain mostly different between each other motifs and most similar within any Layer

```{r}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(ggpubr)
library("readxl")
library(datasets)  
library(UpSetR)
library(VennDiagram)
library(repurrrsive) #for list length

```
-read motifs Excel files: Enh DMR DAR

-read motifs  Enhs

```{r}
#-----------------Enhancers weis

#read_excel("C:/Users/ia1/Documents/irina_docs/EpiGeVar/MayJune2020_egv/DARs_Carine/wei_ecto.xlsx")->motifs_EnhancerEc1
#motifs_EnhancerEc1

read_excel("data_motifs_Carine/wei_ecto.xlsx")->motifs_EnhancerEc1
motifs_EnhancerEc1

read_excel("data_motifs_Carine/wei_endo.xlsx")->motifs_EnhancerEn1
#motifs_EnhancerMes1

read_excel("data_motifs_Carine/wei_meso.xlsx")->motifs_EnhancerMes1
#motifs_EnhancerMes1


```


-read motifs  DMR

```{r}
#-----------------DMRs 

read_excel("data_motifs_Carine/wei_ecto.xlsx")->motifs_DMREc1
#motifs_DMRMes1

read_excel("data_motifs_Carine/wei_endo.xlsx")->motifs_DMREn1
#motifs_DMRMes1

read_excel("data_motifs_Carine/wei_meso.xlsx")->motifs_DMRMes1
#motifs_DMRMes1

```
-read motifs DARs
```{r}

read_excel("data_motifs_Carine/DAR_ecto.xlsx")->motifs_DAREc1

read_excel("data_motifs_Carine/DAR_endo.xlsx")->motifs_DAREn1
#motifs_DARMes


read_excel("data_motifs_Carine/DAR_meso.xlsx")->motifs_DARMes1
#motifs_DARMes1

```
-B. set quantile thresholds for each Layer regions

-B.DMR   quantiles DMR
```{r}
quantile(motifs_DMREc1$P)->q_dmr_ec
quantile(motifs_DMREn1$P)->q_dmr_en
quantile(motifs_DMRMes1$P)->q_dmr_m
q_dmr_ec
q_dmr_en
q_dmr_m

```

-set thr DMR,  quantiles Q75%
```{r}
thrPe_ec2<-q_dmr_ec[4]
thrPe_en2<-q_dmr_en[3]# to make a little smaller
thrPe_m2<-q_dmr_m[4]

```
-make individual lists for DMRs: get the functions

```{r}
source("make_filterP_list_dmrEc.R")
source("make_filterP_list_dmrEn.R")
source("make_filterP_list_dmrM.R")
```
- upsetR plot DMRs
-how similar dmr motifs are bw layers, thrP quantile

```{r}
#-----------------------Q75 thr

vdmrec2<-make_filterP_list_dmrEc(motifs_DMREc1,thrPe_ec2)
#library(repurrrsive)
vdmrec2%>%
map(length)
#typeof(vdmrec)

vdmren2<-make_filterP_list_dmrEn(motifs_DMREn1,thrPe_en2)
vdmren2%>%
map(length)

vdmrm2<-make_filterP_list_dmrM(motifs_DMRMes1,thrPe_m2)
vdmrm2%>%
map(length)
```
- upsetR plot DMRs
-how similar dmr motifs are bw layers, thrP quantile
```{r}
listik_dmr_EcEnM2=c(vdmrec2,vdmren2,vdmrm2)
upset(fromList(listik_dmr_EcEnM2),empty.intersections = "on")
#----------list of motifs
#vdmrec2
#vdmren2


```

-B.DAR   quantiles DAR
```{r}
quantile(motifs_DAREc1$P)->q_dar_ec
quantile(motifs_DAREn1$P)->q_dar_en
quantile(motifs_DARMes1$P)->q_dar_m
q_dar_ec
q_dar_en
q_dar_m

```

-set thr DAR,  quantiles Q25%
```{r}
thrPe_ec2<-q_dar_ec[2]
thrPe_en2<-q_dar_en[2]# to make a little smaller
thrPe_m2<-q_dar_m[2]

```
-make individual lists for DARs: get the functions

```{r}
source("make_filterP_list_darEc.R")
source("make_filterP_list_darEn.R")
source("make_filterP_list_darM.R")

```
- upsetR plot DARs
-how similar dmr motifs are bw layers, thrP quantile

```{r}
#-----------------------Q75 thr

vdarec2<-make_filterP_list_darEc(motifs_DAREc1,thrPe_ec2)
#library(repurrrsive)
vdarec2%>%
map(length)
#typeof(vdarec)

vdaren2<-make_filterP_list_darEn(motifs_DAREn1,thrPe_en2)
vdaren2%>%
map(length)

vdarm2<-make_filterP_list_darM(motifs_DARMes1,thrPe_m2)
vdarm2%>%
map(length)
```
- upsetR plot DARs
-how similar dar motifs are bw layers, thrP quantile
```{r}
#---------------------should be different mostly
listik_dar_EcEnM2=c(vdarec2,vdaren2,vdarm2)
upset(fromList(listik_dar_EcEnM2),empty.intersections = "on")

```
-B.Wei Enhancers

-quantiles Wei
```{r}
quantile(motifs_EnhancerEc1$P)->q_w_ec
quantile(motifs_EnhancerEn1$P)->q_w_en
quantile(motifs_EnhancerMes1$P)->q_w_m
q_w_ec
q_w_en
q_w_m

```
- change thr, quantiles Q75% Wei
```{r}
thrPe_ec2<-q_w_ec[4]
thrPe_en2<-q_w_en[3]# to make a little smaller
thrPe_m2<-q_w_m[4]

```

-make ind lists for Enhancers Wei
```{r}
source("make_filterP_list_enhEc.R")
source("make_filterP_list_enhEn.R")
source("make_filterP_list_enhM.R")
```

-quntile P-threshold Wei

```{r}
#-----------------------Q75 thr Wei

vwec2<-make_filterP_list_enhEc(motifs_EnhancerEc1,thrPe_ec2)
#library(repurrrsive)
vwec2%>%
map(length)
#typeof(vwec)

vwen2<-make_filterP_list_enhEn(motifs_EnhancerEn1,thrPe_en2)
vwen2%>%
map(length)

vwm2<-make_filterP_list_enhM(motifs_EnhancerMes1,thrPe_m2)
vwm2%>%
map(length)
```

-Ectoderm: Enh DAR DMR regions

```{r}
listik_w_dar_dmr_Ec2=c(vwec2,vdarec2,vdmrec2)
upset(fromList(listik_w_dar_dmr_Ec2),empty.intersections = "on")
```
-get elements Ectoderm
```{r}
overlapEct<-calculate.overlap(listik_w_dar_dmr_Ec2)
#overlapEct
```


-Mesoderm: intersection of Enh DAR DMR
```{r}
listik_w_dar_dmr_M2=c(vwm2,vdarm2,vdmrm2)
upset(fromList(listik_w_dar_dmr_M2),empty.intersections = "on")
```
-get upset elements Mesoderm: inresect, distinct, paiwise
```{r}
overlapMes<-calculate.overlap(listik_w_dar_dmr_M2)
#overlapMes
```


-Endoderm within: intersection of Enh DAR DMR

```{r}
listik_w_dar_dmr_En2=c(vwen2,vdaren2,vdmren2)
upset(fromList(listik_w_dar_dmr_En2),empty.intersections = "on")
```
-get elements Endoderm
```{r}
overlapEnd<-calculate.overlap(listik_w_dar_dmr_En2)
#overlapEnd
```
